% --- LaTeX CV Template - S. Venkatraman ---

% Set document class and font size
\documentclass[letterpaper, 11pt]{article}
\usepackage[utf8]{inputenc}

% Package imports
\usepackage{setspace, longtable, graphicx, hyphenat, hyperref, fancyhdr, ifthen, everypage, enumitem, amsmath, setspace}

% --- Page layout settings ---

% Set page margins
\usepackage[left=1in, right=1in, bottom=0.7in, top=0.7in]{geometry}

% Set line spacing
\renewcommand{\baselinestretch}{1.1}

% --- Page formatting ---

% Set link colors
\usepackage[dvipsnames]{xcolor}
\definecolor{accent}{HTML}{264D7E} % deep indigo blue for sections and links
\hypersetup{colorlinks=true, linkcolor=accent, urlcolor=accent}

% Set font to Libertine, including math support
\usepackage{libertine}
\usepackage[libertine]{newtxmath}
\usepackage[tracking=true]{microtype}

% Remove page numbering
\pagenumbering{gobble}

% Section label macro: unified deep navy, slightly larger
\newcommand{\sectionlabel}[1]{\nohyphens{\large\color{accent}{\renewcommand{\arraystretch}{0.9}\begin{tabular}[t]{@{}l@{}}#1\end{tabular}}}}

\newenvironment{cvitems}
{
\begin{itemize}[leftmargin=1.5em,
                itemsep=0pt,
                parsep=0pt,
                topsep=2pt,
                partopsep=0pt]
}
{
\end{itemize}
}

% --- Document starts here ---

\begin{document}

% Name and date of last update to this document
\noindent{\Huge{Jaeyong Ko}
\hfill{\it\footnotesize Updated \today}}

% --- Contact information and other items ---

\vspace{0.5cm} 
\begin{center}
\begin{tabular}{lll}
% Line 1: Email, GitHub, office location
\textbf{Email}: \href{mailto:jyko22@snu.ac.kr}{jyko22@snu.ac.kr}      &
\hspace{0.50in} \textbf{GitHub}: \href{https://github.com/beaver-22}{beaver-22}    &
\hspace{0.50in} \textbf{LinkedIn}: \href{https://www.linkedin.com/in/jaeyong-ko-360870243/}{jaeyong-ko-360870243} \\

\end{tabular}
\end{center}

% --- Start the two-column table storing the main content ---

% Set spacing between columns
\setlength{\tabcolsep}{8pt}

% Set the width of each column
\begin{longtable}{p{1.3in}p{4.8in}}

% --- Section: Research interests ---

\smash{\sectionlabel{Research interests}}
& Large Language Models (LLMs): Mathematical \& Latent Reasoning, and Evaluation in the Financial Domain \\
& \\

% --- Section: Education ---

\smash{\sectionlabel{Education}}
& \textbf{Seoul National University} \hfill Seoul, South Korea \newline
MS in Industrial Engineering \hfill Sep 2025 -- Present \newline
BS in Industrial Engineering \hfill Mar 2019 -- Aug 2025 \newline
\textit{Overall GPA: 3.82/4.3 (3.72/4.0), Major GPA: 3.82/4.3 (3.72/4.0)} \\
& \\

% --- Section: Awards, scholarships, etc. ---

%\sectionlabel{Honors and scholarships}
%& Startup Competition Excellence Award \hfill 2019\\
%& IE Idea Competition Excellence Award (KIIE) \hfill Aug 2019 \\
%& \\

% --- Section: Publications ---
\smash{\sectionlabel{Publications}}
& \textbf{Cliff Tokens: Identifying Single-Token Failure Triggers in LLM Mathematical Reasoning} \newline
\underline{Jaeyong Ko}, Pilsung Kang, Yukyung Lee$^{\dagger}$. \newline
\textit{arXiv preprint arXiv:2606.25524}, 2026. \href{https://arxiv.org/abs/2606.25524}{[arXiv]}
%\textit{Under review} \\
& \\

% --- Section: Research experience ---

\smash{\sectionlabel{Research\\experience}}
& \textbf{Data Science \& Business Analytics Lab, SNU} \hfill Sep 2025 -- Present \newline
Master's Student (Advisor: \href{https://dsba.snu.ac.kr/professor/}{Prof. Pilsung Kang})  \\
& \\

& \textbf{École Polytechnique de Montréal} \hfill Apr 2024 -- Aug 2024 \newline
Research Intern (Advisor: \href{https://www.polymtl.ca/expertises/en/jomaa-walid}{Prof. Walid Jomaa})
\begin{cvitems}
\item Human-centric Smart Manufacturing Workcells for Industry 5.0 applications.
\end{cvitems}
\\
& \\

& \textbf{Financial Engineering Lab, KAIST} \hfill Dec 2023 -- Feb 2024 \newline
Research Intern (Advisor: \href{https://felab.kaist.ac.kr/team.html}{Prof. Woo Chang Kim}) 
\begin{cvitems} 
\item Reinforcement learning applications for goal-based wealth management. 
\end{cvitems}
\\
& \\

% --- Section: Projects ---

\smash{\sectionlabel{Projects}}

& \textbf{Duo 2.0: Evaluating LLM Reliability in Long Financial Conversations}
\,\textbar\, \textit{Granted by Kakaobank}
\hfill Dec 2025 -- Present
\begin{cvitems}
\item Quantified LLM capabilities in resolving ambiguous user queries using LLM-as-a-Judge methodologies.
\item Designed a financial life-cycle event conversation benchmark for evaluating domain-specific conversational reliability.
\end{cvitems}
\\
& \\

& \textbf{Development of Advanced Integrated Monitoring Technologies for Laser Welding}
\,\textbar\, \textit{Granted by LG Electronics}
\hfill Jul 2025 -- Dec 2025
\begin{cvitems}
\item Designed and conducted experiments for a laser welding anomaly detection model utilizing time-series and image multi-modal data.
\end{cvitems}
\\
& \\

% --- Section: Industry experience ---

\smash{\sectionlabel{Industry\\experience}}

& \textbf{EXGRAM} \hfill Jul 2022 -- Oct 2022 \newline
Product Manager Intern
\begin{cvitems}
\item Planned app configurations and push notifications for the app, Veloo.
\end{cvitems}
\\
& \\

& \textbf{SNU Startup Consulting Group (\href{https://www.snuact.org/}{ACT})}
\hfill Mar 2023 -- Dec 2023 \newline
President \& Team member
\begin{cvitems}
\item Led a student consulting group and secured four startup consulting engagements with \textit{Moderntec}, \textit{Designovel}, \textit{Spring Onward}, and \textit{Sweetspot}.
\item Developed GTM strategies for \textit{Designovel} (AI fashion-tech), \textit{Moderntec} (EV charging infrastructure), and \textit{Wavebridge} (cryptocurrency OTC platform).
\end{cvitems}
\\
& \\

% --- Section: Teaching experience ---

\smash{\sectionlabel{Teaching\\experience}}

& \textbf{Peer Tutoring, Seoul National University} \newline
Course: Production Control (406.310) \hfill Sep 2024 -- Dec 2024 \newline
Course: Human Factors Engineering (406.304) \hfill Sep 2023 -- Dec 2023 \\
& \\

% --- Section: Various skills (programming, software, languages, etc.) ---

\smash{\sectionlabel{Skills}}
& \textbf{Programming and Software}\newline
Proficient in: Python, R, MySQL, Docker, Git, vLLM, \LaTeX. \\
& \\

& \textbf{Languages} \newline
Native Korean; Professional working proficiency in English (OPIc IH). \\
& \\

% --- Section: Military Service ---

\smash{\sectionlabel{Military service}}
& \textbf{Republic of Korea Army} \hfill Jan 2021 -- Jul 2022 \newline
Corporal
\begin{cvitems}
\item Completed full-term mandatory military service, demonstrating adaptability, discipline, and leadership through various operational trainings.
\end{cvitems}
\\
& \\

% --- Section: Other interests/hobbies ---

% \smash{\sectionlabel{Other interests}} & Marathon running, dinghy sailing (ILCA 7), soccer, road cycling\\

% --- End of CV! ---

\end{longtable}
\end{document}